Open science and the future university researcher\thanks{This work is licensed under a \href{https://creativecommons.org/licenses/by/4.0/}{Creative Commons Attribution 4.0 International License} \ccby}

### 2017-02-07 paper-imagine-new-university.tex
beginning of challenges section

To me, working openly should be the default mode of science---after all, how can
we advance knowledge ``by standing on the shoulders of giants''\footnote{``If I
have seen further, it is by standing on the shoulders of giants.'' Isaac
Newton, 1676, although similar statements can be found as far back as the 12th
century.} if we cannot access or see those shoulders?

@@

Since then, I have adopted the following policy for my group's research:
\begin{itemize}
    \item All written research products are made openly accessible, either through
    green or gold open-access avenues. Since my field generally lacks recognized,
    fully open-access journals, this objective is typically met by submitting
    preprints to services such as arXiv, engrXiv, or PeerJ Preprints, depending
    on the paper's topic. Conference papers, when not submitted to an open venue,
    are also made openly available through, e.g., Figshare. Where possible, all
    preprints will be released under the CC-BY license.
    (I choose, in general, to not follow the hybrid gold open-access model by
    paying a non-fully open journal.)

@@

In addition to these standards

\section{Institutional challenges to open science}

>>>>

To me, working openly should be the default mode of science---after all, how can
we advance knowledge ``by standing on the shoulders of giants''\footnote{``If I
have seen further, it is by standing on the shoulders of giants.'' Isaac
Newton (1676), although similar statements can be found as far back as the 12th
century.} if we cannot access or see those shoulders?

@@

Since then, I have adopted the following policy for my group's research:
\begin{itemize}
    \item All written research products are made openly accessible, either through
    green or gold open-access avenues. Since my field generally lacks recognized,
    fully open-access journals, this objective is typically met by submitting
    preprints to services such as arXiv, engrXiv, or PeerJ Preprints, depending
    on the paper's topic. Conference papers, when not submitted to an open venue,
    are also made openly available through, e.g., Figshare. Where possible, all
    preprints will be released under the Creative Commons Attribution (CC-BY)
    license.\footnote{\url{https://creativecommons.org/licenses/by/4.0/legalcode}}
    (I choose, in general, to not follow the hybrid gold open-access model by
    paying a non-fully open journal.)

@@

In addition to these standards I established for my and my group's research, I
have also gotten involved with and helped initiate some community efforts to
encourage and reward open science practices.

First, after participating in the working group on software credit at the Third
Workshop on Sustainable Software for Science: Practice and Experiences
(WSSSPE3)\autocite{Katz:2016er}, I joined the FORCE11 Software Citation Working
Group as a cochair, and helped coauthor the resulting Software Citation
Principles\autocite{Smith:2016kt}. One purpose of standardizing software
citation is to help ensure authors\slash developers receive academic credit for
their work in releasing open research software. I also serve on the editorial
boards of the \textit{Journal of Open Research
Software} and \textit{Journal of Open Source Software}\footnote{\url{http://joss.theoj.org/};
\url{http://openresearchsoftware.metajnl.com/}},
which offer publication venues focused solely on open-source research software.

I have also collaborated with colleagues in engineering fields to improve
venues for open-access publications. I serve on the editorial board of
\textit{The Journal of Open Engineering},
and published an editorial discussing the importance of open publishing in
engineering\autocite{TJOE:editorial}. With some of the same collaborators, I
helped initiate engrXiv\footnote{\url{http://engrxiv.org}}, an open archive
for engineering publications, inspired by the arXiv.

\section{Challenges to performing open science}
\label{sec:challenges}

In my view, the challenges impeding greater adoption of open-science practices
are mainly institutional and cultural, rather than technical. General venues for sharing
and developing the products of research openly abound these days, with the availability
of services like arXiv, engrXiv, and PeerJ Preprints for ensuring open access of
publications; repositories like GitHub for developing (and version-controlling)
research software openly; and data and software archives like Zenodo and Figshare,
which practically have no file size limitations.\footnote{Zenodo currently accepts
datasets up to 50GB, but stores data in the CERN Data Center, along with 100PB of
physics data from the Large Hadron Collider (\url{https://zenodo.org/faq}).}
Of course, some technical problems remain: How do we make results of computational
science, particularly when it involves demanding high-performance computing resources,
truly reproducible? How can we cite software and data consistently, when
the version might change regularly?

Instead, cultural inertia and lack of institutional recognition\slash rewards pose
the most significant challenges to increased openness in science.
